### 2017-10-17 Appendix.tex
updated TreeLevelPlots

\subsection{Constants of the Color Algebra $SU(N)$}\label{sec:coloralgebra}
Tha Casimir operator $C(R)\mathbbm{1}$ of a semi-simple Lie algebra in the irreducible representation $R$ is given by\cite{Marina}
\begin{align}
g^{ab} T^a(R)T^b(R) = C(R)\mathbbm{1}, \label{eq:Casimir}
\end{align}
where $T^a(R)$ is the $a$-th generator of the matrix valued representation $R$, $g^{ab}$ is the metric of the group, $C(R)$ is the quadratic Casimir invariant of the representation $R$ and $\mathbbm{1}$ is the identity in the representation space.\\
Apart from $C(R)$ it is common to define the Dynkin-Index $T(R)$:
\begin{align}
\mathrm{Tr}\left[T^a(R)T^b(R)\right] = T(R)\delta^{ab}.
\end{align}
The two constants are connected by
\begin{align}
C(R) \cdot \mathrm{dim}(R) = T(R) \cdot \mathrm{dim}(G),
\end{align}
where $\mathrm{dim}(G)$ is the dimension of the group and $\mathrm{dim}(R)$ is the dimension of the irreducible representation $R$.\\
In the case of $SU(N)$ one has a diagonal metric $g^{ab} = \delta^{ab}$ and therefore eq. \ref{eq:Casimir} turns to
\begin{align}
\sum_a (T^a(R))^2 = C(R)\mathbbm{1}_{\mathrm{dim}(R) \times \mathrm{dim}(R)}
\end{align}
and one can write down the following useful formulae for the fundamental representation $R=F$: $T^a_{ij} = \frac{\lambda^a_{ij}}{2}$ and the adjoint representation $R=A$: $(T^a_{ij})^{adj} = -if_{aij}$:
\begin{align}
T^a_{ik} T^a_{kj} &= C(F)\mathbbm{1}_{ij} && \mbox{with}\ C(F) = \frac{N^2-1}{2N} = \frac{4}{3},\nonumber\\
f^{abc} f^{dbc} &= C(A)\delta^{ad} && \mbox{with}\ C(A) = N = 3,\nonumber\\
\mathrm{Tr}\left[T^aT^b\right] &= T(F)\delta^{ab} && \mbox{with}\ T(F) = \frac{1}{2},\label{eq:DynkinIndex}
\end{align}
where $\lambda^a_{ij}$ are for $N_c = 3$ the Gell-Mann matrices and $f_{abc}$ are the structure constants of $SU(N_c)$.
%\begin{tabular}{c|c|c}
%Quadratic Casimir Invariant and $T(R)$ & $SU(N)_c$ & $SU(3)_c$\\
%\hline
%$C_2(3)$ & $\frac{N^2-1}{2N}$ & $\frac{4}{3}$\\
%$C_2(8)$ & $N$ & $3$\\
%$T(3)$ & $\frac{1}{2}$ & $\frac{1}{2}$ \\
%$T(8)$ & $N$ & $3$ 
%\end{tabular}

@@

\subsection{Feynman Rules for the RSQCD}\label{sec:FeynmanRules}
The following Feynman rules (fig. \ref{fig:firstFeynmanRules} - \ref{fig:thirdFeynmanRules}) are derived from the Lagrangian of the $R$-symmetric supersymmetric quantum chromodynamics (RSQCD) eq. \eqref{eq:L_RSQCD}. When compared with the Feynman rules of the supersymmetric QCD the diagrams involving scalar gluons are new. In addition the gluon-quark-squark vertex is different in RSQCD for the gauginos are Dirac fermions. Note that for calculations involving fermions one needs to multiply the Feynman rules in the opposite direction of the fermion flow which is given by a curved arrow next to the diagrams in fig. \ref{fig:secondFeynmanRules} and does not always agree with the flow of fermion number given by the direction of the Dirac propagator. This renders the evaluation of fermion number violating processes like $qq \to \tilde{q}\tilde{q}$ unambiguous, cf. \cite{Beenakker:1996ch}.
%refer to paper cited in Beenakker(Appendix: Feynmanrules)
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\node at (-0.5,0.7) {\circled{1}};	
	\draw[scalarnoarrow](0,0)--(1.5,0);
	\node at (180:0.4) {$(\sigma^0)^a$};
	\node at (0:1.9) {$(\sigma^0)^b$};
	\node at (3.4,0) {$\hat{=}\ \frac{i}{p^2-m_{\sigma^0}^2+i\varepsilon}\delta_{ab}$};
\begin{scope}[shift={(7,0)}]
	\node at (-0.5,0.7) {\circled{2}};
	\draw[scalarnoarrow](0,0)--(1.5,0);
	\node at (180:0.4) {$(\phi^0)^a$};
	\node at (0:1.9) {$(\phi^0)^b$};
	\node at (3.4,0) {$\hat{=}\ \frac{i}{p^2-m_{\phi^0}^2+i\varepsilon}\delta_{ab}$};
\end{scope}
\begin{scope}[shift={(0,-2)}]
	\node at (-0.5,0.7) {\circled{3}};
	\draw[scalarbar](0,0)--(1.5,0);
	\node at (180:0.3) {$\tilde{q}_{Ai}$};
	\node at (0:1.8) {$\tilde{q}_{Bj}^\dagger$};
	\node at (3,0) {$\hat{=}\ \frac{i\delta_{AB}}{p^2-m_{\tilde{q}}^2+i\varepsilon}\delta_{ij}$};
\end{scope}
\begin{scope}[shift={(7,-2)}]
	\node at (-0.5,0.7) {\circled{4}};
	\draw[fermionbar](0,0)--(1.5,0);
	\node at (180:0.2) {$q_i$};
	\node at (0:1.7) {$\overline{q}_j$};
	\node at (3,0) {$\hat{=}\ i\frac{\slashed{p}+m_q}{p^2-m_q^2+i\varepsilon}\delta_{ij}$};
\end{scope}
\begin{scope}[shift={(0,-4)}]
	\draw[gluon](1.5,0)--(0,0);
	\node at (-0.5,0.7) {\circled{5}};
	\node at (180:0.2) {$G_\mu^a$};
	\node at (0:1.7) {$G_\nu^b$};
	\node at (3,0) {$\hat{=}\ -i\frac{g^{\mu\nu}}{p^2+i\varepsilon}\delta_{ab}$};
\end{scope}
\begin{scope}[shift={(7,-4)}]
	\node at (-0.5,0.7) {\circled{6}};
	\draw[gluon](1.5,0)--(0,0);
	\draw[fermionnoarrow](0,0)--(1.5,0);
	\node at (180:0.2) {$\tilde{g}^a$};
	\node at (0:1.7) {$\overline{\tilde{g}}^b$};
	\node at (3,0) {$\hat{=}\ i\frac{\slashed{p}+m_{\tilde{g}}}{p^2-m_{\tilde{g}}^2+i\varepsilon}\delta_{ab}$};
\end{scope}
\begin{scope}[shift={(0,-6)}]
	\node at (-0.5,0.7) {\circled{7}};
	\draw[ghostbar](0,0)--(1.5,0);
	\node at (180:0.3) {$c^{a}$};
	\node at (0:1.8) {$\overline{c}^{b}$};
	\node at (3,0) {$\hat{=}\ \frac{i}{p^2+i\varepsilon}\delta_{ab}$};
\end{scope}

\begin{scope}[shift={(1,-8)}]
	\node at (-1.5,0.7) {\circled{8}};
	\draw[fermion] (0,0)--(45:1);
	\draw[fermionbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.3) {$\overline{q}_i$};
	\node at (-45:1.3) {$q_j$};
	\node at (180:1.3) {$G_\mu^a$};
	\node at (2,0) {$\hat{=} -ig_s T^a_{ij}\gamma^\mu$};
\end{scope}
\begin{scope}[shift={(8,-8)}]
	\node at (-1.5,0.7) {\circled{9}};
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.4) {$\tilde{q}^\dagger_{Ai}(-p_1)$};
	\node at (-45:1.4) {$\tilde{q}_{Bj}(p_2)$};
	\node at (180:1.3) {$G_\mu^a$};
	\node at (3,0) {$\hat{=} -ig_s (p_2+p_1)^\mu T^a_{ij}\delta_{AB}$};
\end{scope}
\begin{scope}[shift={(1,-10.5)}]
	\node at (-1.5,0.7) {\circled{10}};
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(135:1);
	\draw[gluon] (0,0)--(-135:1);
	\node at (45:1.4) {$\tilde{q}^\dagger_{Ai}$};
	\node at (-45:1.4) {$\tilde{q}_{Bj}$};
	\node at (135:1.4) {$G_\mu^a$};
	\node at (-135:1.4) {$G_\nu^b$};
	\node at (3,0) {$\hat{=} \ ig_s^2 g^{\mu\nu} \left\{T^a,T^b\right\}_{ij}\delta_{AB}$};
\end{scope}
\begin{scope}[shift={(1,-13.5)}]
	\node at (-1.5,0.7) {\circled{11}};
	\draw[gluon] (0,0)--(45:1);
	\draw[gluon] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.4) {$G_\mu^a(p_a)$};
	\node at (-45:1.4) {$G_\nu^b(p_b)$};
	\node at (180:1.5) {$G_\rho^c(p_c)$};
	\node at (5.5,0) {$\hat{=}  - g_s f_{abc} \left[ g_{\mu\nu}(p_a-p_b)^\rho +\  g_{\nu\rho}(p_b-p_c)^\mu +  g_{\rho\mu}(p_c-p_a)^\nu \right]$};
\end{scope}
\end{tikzpicture}
\caption{In the Feynman diagrams of the propagators the momentum is flowing from the right to the left hand side. The gluon propagator is given in Feynman gauge.\newline
In the Feynman diagrams of the vertices all momenta flow towards the vertex, i.e. in diagram 9: $-p_1$ flows towards the vertex.\newline
The indices $A,B \in \left\{ L,R \right\}$ label the left/right ``handedness'' of the squarks. The indices $i,j=1,2,3$ are the color indices in the (anti)fundamental representation where $a,b,c,\hdots = 1,\hdots,8$ are the color indices of the adjoint representation.}\label{fig:firstFeynmanRules}
\end{center}
\end{figure}
\newpage

@@

	\path[line width=0.8pt,<-] (g) edge [out=135, in=-135] (gbar);

@@

	\path[line width=0.8pt,<-] (g) edge [out=0, in=135] (u);

@@

	\path[line width=0.8pt,->] (g) edge [out=0, in=225] (u);

@@

	\node at (3,0) {$\hat{=} \ -g_s^2 (f^{abc}f^{ade} + f^{abc}f^{adc})$};

@@

&\frac{1}{4}\Theta(tu-4m_1^2m_2^2)\delta \left(s+t+u-m_1^2-m_2^2\right)

>>>>

\subsection{Constants of the Color Algebra $SU(N)$}\label{sec:coloralgebra}
Tha Casimir operator $C(R)\mathbbm{1}$ of a semi-simple Lie algebra in the irreducible representation $R$ is given by\cite{Marina}
\begin{align}
g^{ab} T^a(R)T^b(R) = C(R)\mathbbm{1}, \label{eq:Casimir}
\end{align}
where $T^a(R)$ is the $a$-th generator of the matrix valued representation $R$, $g^{ab}$ is the metric of the group, $C(R)$ is the quadratic Casimir invariant of the representation $R$ and $\mathbbm{1}$ is the identity in representation space.\\
Apart from $C(R)$ it is common to define the Dynkin-Index $T(R)$:
\begin{align}
\mathrm{Tr}\left[T^a(R)T^b(R)\right] = T(R)\delta^{ab}.
\end{align}
The two constants are connected by
\begin{align}
C(R) \cdot \mathrm{dim}(R) = T(R) \cdot \mathrm{dim}(G),
\end{align}
where $\mathrm{dim}(G)$ is the dimension of the group and $\mathrm{dim}(R)$ is the dimension of the irreducible representation $R$.\\
In the case of $SU(N)$ one has a diagonal metric $g^{ab} = \delta^{ab}$ and therefore eq. \ref{eq:Casimir} turns to
\begin{align}
\sum_a (T^a(R))^2 = C(R)\mathbbm{1}_{\mathrm{dim}(R) \times \mathrm{dim}(R)}
\end{align}
and one can write down the following useful formulae for the fundamental representation $R=F$: $T^a_{ij} = \frac{\lambda^a_{ij}}{2}$ and the adjoint representation $R=A$: $(T^a_{ij})^{adj} = -if_{aij}$:
\begin{align}
T^a_{ik} T^a_{kj} &= C(F)\mathbbm{1}_{ij} && \mbox{with}\ C(F) = \frac{N^2-1}{2N} = \frac{4}{3},\nonumber\\
f^{abc} f^{dbc} &= C(A)\delta^{ad} && \mbox{with}\ C(A) = N = 3,\nonumber\\
\mathrm{Tr}\left[T^aT^b\right] &= T(F)\delta^{ab} && \mbox{with}\ T(F) = \frac{1}{2},\label{eq:DynkinIndex}
\end{align}
where $\lambda^a_{ij}$ are for $N_c = 3$ the Gell-Mann matrices and $f_{abc}$ are the structure constants of $SU(N_c)$, defined in eq. \eqref{eq:struc_const}.
%\begin{tabular}{c|c|c}
%Quadratic Casimir Invariant and $T(R)$ & $SU(N)_c$ & $SU(3)_c$\\
%\hline
%$C_2(3)$ & $\frac{N^2-1}{2N}$ & $\frac{4}{3}$\\
%$C_2(8)$ & $N$ & $3$\\
%$T(3)$ & $\frac{1}{2}$ & $\frac{1}{2}$ \\
%$T(8)$ & $N$ & $3$ 
%\end{tabular}

@@

\subsection{Feynman Rules for the RSQCD}\label{sec:FeynmanRules}
The following Feynman rules (fig. \ref{fig:firstFeynmanRules} - \ref{fig:thirdFeynmanRules}) are derived from the Lagrangian of the $R$-symmetric supersymmetric quantum chromodynamics (RSQCD) eq. \eqref{eq:L_RSQCD}. When compared with the Feynman rules of the supersymmetric QCD the diagrams involving scalar gluons are new. In addition the gluon-quark-squark vertex is different in RSQCD for the gauginos are Dirac fermions. Note that for calculations involving fermions one needs to multiply the Feynman rules in the opposite direction of the fermion flow which is given by a curved arrow next to the diagrams in fig. \ref{fig:secondFeynmanRules} and does not always agree with the flow of fermion number given by the direction of the Dirac propagator. This renders the evaluation of fermion number violating processes like $qq \to \tilde{q}\tilde{q}$ unambiguous, cf. \cite{Beenakker:1996ch}.
%refer to paper cited in Beenakker(Appendix: Feynmanrules)
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[line width=1.5 pt, scale=1.3]
	\node at (-0.5,0.7) {\circled{1}};	
	\draw[scalarnoarrow](0,0)--(1.5,0);
	\node at (180:0.4) {$(\sigma^0)^a$};
	\node at (0:1.9) {$(\sigma^0)^b$};
	\node at (3.4,0) {$\hat{=}\ \frac{i}{p^2-m_{\sigma^0}^2+i\varepsilon}\delta_{ab}$};
\begin{scope}[shift={(7,0)}]
	\node at (-0.5,0.7) {\circled{2}};
	\draw[scalarnoarrow](0,0)--(1.5,0);
	\node at (180:0.4) {$(\phi^0)^a$};
	\node at (0:1.9) {$(\phi^0)^b$};
	\node at (3.4,0) {$\hat{=}\ \frac{i}{p^2-m_{\phi^0}^2+i\varepsilon}\delta_{ab}$};
\end{scope}
\begin{scope}[shift={(0,-2)}]
	\node at (-0.5,0.7) {\circled{3}};
	\draw[scalarbar](0,0)--(1.5,0);
	\node at (180:0.3) {$\tilde{q}_{Ai}$};
	\node at (0:1.8) {$\tilde{q}_{Bj}^\dagger$};
	\node at (3,0) {$\hat{=}\ \frac{i\delta_{AB}}{p^2-m_{\tilde{q}}^2+i\varepsilon}\delta_{ij}$};
\end{scope}
\begin{scope}[shift={(7,-2)}]
	\node at (-0.5,0.7) {\circled{4}};
	\draw[fermionbar](0,0)--(1.5,0);
	\node at (180:0.2) {$q_i$};
	\node at (0:1.7) {$\overline{q}_j$};
	\node at (3,0) {$\hat{=}\ i\frac{\slashed{p}+m_q}{p^2-m_q^2+i\varepsilon}\delta_{ij}$};
\end{scope}
\begin{scope}[shift={(0,-4)}]
	\draw[gluon](1.5,0)--(0,0);
	\node at (-0.5,0.7) {\circled{5}};
	\node at (180:0.2) {$G_\mu^a$};
	\node at (0:1.7) {$G_\nu^b$};
	\node at (3,0) {$\hat{=}\ -i\frac{g^{\mu\nu}}{p^2+i\varepsilon}\delta_{ab}$};
\end{scope}
\begin{scope}[shift={(7,-4)}]
	\node at (-0.5,0.7) {\circled{6}};
	\draw[gluon](1.5,0)--(0,0);
	\draw[fermionnoarrow](0,0)--(1.5,0);
	\node at (180:0.2) {$\tilde{g}^a$};
	\node at (0:1.7) {$\overline{\tilde{g}}^b$};
	\node at (3,0) {$\hat{=}\ i\frac{\slashed{p}+m_{\tilde{g}}}{p^2-m_{\tilde{g}}^2+i\varepsilon}\delta_{ab}$};
	\path[line width=0.8pt,>-] (0.25,-0.3) edge [out=180, in=0](1.25,-0.3);
\end{scope}
\begin{scope}[shift={(0,-6)}]
	\node at (-0.5,0.7) {\circled{7}};
	\draw[ghostbar](0,0)--(1.5,0);
	\node at (180:0.3) {$c^{a}$};
	\node at (0:1.8) {$\overline{c}^{b}$};
	\node at (3,0) {$\hat{=}\ \frac{i}{p^2+i\varepsilon}\delta_{ab}$};
\end{scope}

\begin{scope}[shift={(1,-8)}]
	\node at (-1.5,0.7) {\circled{8}};
	\draw[fermion] (0,0)--(45:1);
	\draw[fermionbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.3) {$\overline{q}_i$};
	\node at (-45:1.3) {$q_j$};
	\node at (180:1.3) {$G_\mu^a$};
	\node at (2,0) {$\hat{=} -ig_s T^a_{ij}\gamma^\mu$};
\end{scope}
\begin{scope}[shift={(8,-8)}]
	\node at (-1.5,0.7) {\circled{9}};
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.4) {$\tilde{q}^\dagger_{Ai}(-p_1)$};
	\node at (-45:1.4) {$\tilde{q}_{Bj}(p_2)$};
	\node at (180:1.3) {$G_\mu^a$};
	\node at (3,0) {$\hat{=} -ig_s (p_2+p_1)^\mu T^a_{ij}\delta_{AB}$};
\end{scope}
\begin{scope}[shift={(1,-10.5)}]
	\node at (-1.5,0.7) {\circled{10}};
	\draw[scalar] (0,0)--(45:1);
	\draw[scalarbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(135:1);
	\draw[gluon] (0,0)--(-135:1);
	\node at (45:1.4) {$\tilde{q}^\dagger_{Ai}$};
	\node at (-45:1.4) {$\tilde{q}_{Bj}$};
	\node at (135:1.4) {$G_\mu^a$};
	\node at (-135:1.4) {$G_\nu^b$};
	\node at (3,0) {$\hat{=} \ ig_s^2 g^{\mu\nu} \left\{T^a,T^b\right\}_{ij}\delta_{AB}$};
\end{scope}
\begin{scope}[shift={(8,-10.5)}]
	\node at (-1.5,0.7) {\circled{10a}};
	\draw[ghost] (0,0)--(45:1);
	\draw[ghostbar] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.4) {$\overline{c}^a(-p_1)$};
	\node at (-45:1.4) {$c^c$};
	\node at (180:1.3) {$G_\mu^b$};
	\node at (3,0) {$\hat{=} -g_s f^{abc}p_1^\mu$};
\end{scope}
\begin{scope}[shift={(1,-13.5)}]
	\node at (-1.5,0.7) {\circled{11}};
	\draw[gluon] (0,0)--(45:1);
	\draw[gluon] (0,0)--(-45:1);
	\draw[gluon] (0,0)--(180:1);
	\node at (45:1.4) {$G_\mu^a(p_a)$};
	\node at (-45:1.4) {$G_\nu^b(p_b)$};
	\node at (180:1.5) {$G_\rho^c(p_c)$};
	\node at (5.5,0) {$\hat{=}  - g_s f_{abc} \left[ g_{\mu\nu}(p_a-p_b)^\rho +\  g_{\nu\rho}(p_b-p_c)^\mu +  g_{\rho\mu}(p_c-p_a)^\nu \right]$};
\end{scope}
\end{tikzpicture}
\caption{In the Feynman diagrams of the propagators the momentum is flowing from the right to the left hand side. The gluon propagator is given in Feynman gauge.\newline
In the Feynman diagrams of the vertices all momenta flow towards the vertex, i.e. in diagram 9 and 10a: $-p_1$ flows towards the vertex.\newline
The indices $A,B \in \left\{ L,R \right\}$ label the left/right ``handedness'' of the squarks. The indices $i,j=1,2,3$ are the color indices in the (anti)fundamental representation where $a,b,c,\hdots = 1,\hdots,8$ are the color indices of the adjoint representation.}\label{fig:firstFeynmanRules}
\end{center}
\end{figure}
\newpage

@@

	\path[line width=0.8pt,->] (g) edge [out=135, in=-135] (gbar);

@@

	\path[line width=0.8pt,->] (g) edge [out=0, in=135] (u);

@@

	\path[line width=0.8pt,<-] (g) edge [out=0, in=225] (u);

@@

	\node at (3,0) {$\hat{=} \ ig_s^2 (f^{abc}f^{ade} + f^{abe}f^{adc})$};

@@

&\frac{1}{4}\Theta(tu-m_1^2m_2^2)\delta \left(s+t+u-m_1^2-m_2^2\right)

### 2017-10-17 MSSM.tex
updated TreeLevelPlots

\subsection{Supersymmetry as an Extention of the Poincaré Symmetry}\label{sec:SUSYalgebra}
As already seen in the previous chapter, symmetries are of vital importance when studying particle physics. Coleman and Mandula \cite{Coleman:1967ad} found that for any reasonable quantum field theory space-time and internal symmetries, i.e. gauge symmetries ``cannot by combined in any but the trivial way''\cite{Pelc:1996vg}. Ergo, the symmetry groups of the Standard Model are the most general ones.\\
This statement was corrected by the Haag-{\L}opusza\'nski-Sohnius theorem \cite{Haag:1974qh} which weakened the condition of the quantum field theory by allowing also for anticommuting symmetry generators. This is, by introducing the generators $Q_\alpha$ and $\overline{Q}^{\dot{\alpha}}$ with $\alpha, \dot{\alpha} \in \left\{ 1,2 \right\}$, the Poincare-algebra eq. \eqref{eq:PoincareAlgebra} can be nontrivially extended to the so called superalgebra (see Appendix \eqref{sec:2spinor_notation} for the definition of the $\sigma$-matrices):
\begin{align}
\left\{Q_\alpha,Q_\beta\right\} = \left\{\overline{Q}_{\dot{\alpha}},\overline{Q}_{\dot{\beta}}\right\} &= 0,  \nonumber\\
\left\{Q_\alpha,\overline{Q}_{\dot{\alpha}}\right\} &= 2\sigma^\mu_{\alpha\dot{\alpha}} P_\mu, \nonumber\\
[P^\mu,Q_\alpha] = [P^\mu,\overline{Q}_{\dot{\alpha}}] &= 0, \nonumber \\
[Q_\alpha, J^{\mu\nu}] &= \frac{1}{2} (\sigma^{\mu\nu})_\alpha^{\ \beta} Q_\beta.\label{eq:SUSYalgebra}
\end{align}
As $J^{\mu\nu}$ is the generalized angular momentum operator, the last line in eq. \eqref{eq:SUSYalgebra} implies that $Q_\alpha$ is a spin-$\frac{1}{2}$ operator. Applying $Q_\alpha$ to a field will change the spin of it by $\frac{1}{2}$. This means supersymmetry generators convert fermions to bosons and vice versa.\\
The superalgebra in eq. \eqref{eq:SUSYalgebra} is actually the smallest extension of the Poincare-algebra as it is possible to introduce further anticommuting symmetry generators. Their maximal number is fixed to $N = 8$. Because the MSSM is a minimal extension of the Standard Model, it deals with only one set of anticommuting symmetry generators and is therefore referred to be a $N = 1$ supersymmetric theory.\\
A representation in the form of differential operators can be given by introducing superspace. Superspace is a manifold obtained by enlarging Minkowski space, whose coordinates are labeled with $x^\mu$, with four anticommuting numbers: $\theta^\alpha$ and $\overline{\theta}^{\dot{\alpha}}$, where $\alpha,\ \dot{\alpha} \in \left\{ 1,2 \right\}$ (see Appendix \ref{sec:AnticommNumbers} for the definition of anticommuting numbers). A representation of the superalgebra reads
\begin{align}
P^\mu &= i\partial^\mu,\nonumber\\
J^{\mu\nu} &= i(x^\mu\partial^\nu - x^\nu\partial^\mu),\nonumber\\
Q_\alpha &= i(\partial_\alpha + i\sigma^\mu_{\alpha\dot{\alpha}}
\overline{\theta}^{\dot{\alpha}}\partial_\mu),\nonumber\\
\overline{Q}_{\dot{\alpha}} &= i(-\overline{\partial}_{\dot{\alpha}} - i \theta^\alpha \sigma^\mu_{\alpha\dot{\alpha}}\partial_\mu).\label{eq:SUSYGen}
\end{align}

>>>>

\subsection{Supersymmetry as an Extention of the Poincaré Symmetry}\label{sec:SUSYalgebra}
As already seen in the previous chapter, symmetries are of vital importance when studying particle physics. Coleman and Mandula \cite{Coleman:1967ad} found that for any reasonable quantum field theory space-time and internal symmetries, i.e. gauge symmetries ``cannot by combined in any but the trivial way''\cite{Pelc:1996vg}. Ergo, the symmetry groups of the Standard Model are the most general ones.\\
This statement was corrected by the Haag-{\L}opusza\'nski-Sohnius theorem \cite{Haag:1974qh} which weakened the condition of the quantum field theory by allowing also for anticommuting symmetry generators. This is, by introducing the generators $Q_\alpha$ and $\overline{Q}^{\dot{\alpha}}$ with $\alpha, \dot{\alpha} \in \left\{ 1,2 \right\}$, the Poincare algebra eq. \eqref{eq:PoincareAlgebra} can be nontrivially extended to the so called superalgebra (see Appendix \eqref{sec:2spinor_notation} for the definition of the $\sigma$-matrices):
\begin{align}
\left\{Q_\alpha,Q_\beta\right\} = \left\{\overline{Q}_{\dot{\alpha}},\overline{Q}_{\dot{\beta}}\right\} &= 0,  \nonumber\\
\left\{Q_\alpha,\overline{Q}_{\dot{\alpha}}\right\} &= 2\sigma^\mu_{\alpha\dot{\alpha}} P_\mu, \nonumber\\
[P^\mu,Q_\alpha] = [P^\mu,\overline{Q}_{\dot{\alpha}}] &= 0, \nonumber \\
[Q_\alpha, J^{\mu\nu}] &= \frac{1}{2} (\sigma^{\mu\nu})_\alpha^{\ \beta} Q_\beta.\label{eq:SUSYalgebra}
\end{align}
As $J^{\mu\nu}$ is the generalized angular momentum operator, the last line in eq. \eqref{eq:SUSYalgebra} implies that $Q_\alpha$ is a spin-$\frac{1}{2}$ operator. Applying $Q_\alpha$ to a field will change the spin of it by $\frac{1}{2}$. This means supersymmetry generators convert fermions to bosons and vice versa.\\
The superalgebra in eq. \eqref{eq:SUSYalgebra} is actually the smallest extension of the Poincare algebra as it is possible to introduce further anticommuting symmetry generators. Their maximal number is fixed to $N = 8$. Because the MSSM is a minimal extension of the Standard Model, it deals with only one set of anticommuting symmetry generators and is therefore referred to be a $N = 1$ supersymmetric theory.\\
A representation in the form of differential operators can be given by introducing superspace. Superspace is a manifold obtained by enlarging Minkowski space, whose coordinates are labeled with $x^\mu$, with four anticommuting numbers: $\theta^\alpha$ and $\overline{\theta}^{\dot{\alpha}}$, where $\alpha,\ \dot{\alpha} \in \left\{ 1,2 \right\}$ (see Appendix \ref{sec:AnticommNumbers} for the definition of anticommuting numbers). A representation of the superalgebra reads
\begin{align}
P^\mu &= i\partial^\mu,\nonumber\\
J^{\mu\nu} &= i(x^\mu\partial^\nu - x^\nu\partial^\mu),\nonumber\\
Q_\alpha &= i(\partial_\alpha + i\sigma^\mu_{\alpha\dot{\alpha}}
\overline{\theta}^{\dot{\alpha}}\partial_\mu),\nonumber\\
\overline{Q}_{\dot{\alpha}} &= i(-\overline{\partial}_{\dot{\alpha}} - i \theta^\alpha \sigma^\mu_{\alpha\dot{\alpha}}\partial_\mu).\label{eq:SUSYGen}
\end{align}

### 2017-10-17 Masterarbeit.tex
updated TreeLevelPlots

\pagenumbering{gobble}   % no pagenumbering
% Titelpageseite
\begin{titlepage}
 \begin{tabularx}{\linewidth}{X}
  \includegraphics[width=6cm]{TU_Logo_SW} \\\hline\hline
  \vspace{4.5em}
  \begin{singlespace}\begin{center}\bfseries\Huge  
  Squark Production in the R-Symmetric Supersymmetric Standardmodel  
  \end{center}\end{singlespace}
  \vspace{5.5em}
  \begin{singlespace}\begin{center}\large
   Masterarbeit \\ zur Erlangung des Hochschulgrades \\ 
   Master of Science \\ 
   im Master-Studiengang Physik
  \end{center}\end{singlespace}\medskip
  \begin{center}vorgelegt von\end{center}
  \begin{center}
   {\large Sebastian Liebschner} \\ geboren am 08.05.1990 in Meerane
  \end{center}\medskip
  \begin{singlespace}\begin{center}\large
   Institut für Kern- und Teilchenphysik \\
   Fachrichtung Physik \\
   Fakultät Mathematik und Naturwissenschaften \\
   Technische Universität Dresden \\ 2016
  \end{center}\end{singlespace}
 \end{tabularx}
\end{titlepage}

@@

% Gutachterseite
\thispagestyle{empty}\vspace*{48em}
Eingereicht am 15.~Juli~2016\vspace{1.5em}
\par{\large\begin{tabular}{ll}
 1. Gutachter: & Prof.~Dr.~Dominik Stöckinger \\
 2. Gutachter: & Prof.~Dr.~Arno Straessner \\
\end{tabular}}
\newpage

>>>>

\pagenumbering{gobble}   % no pagenumbering
% Titelpageseite
\begin{titlepage}
 \begin{tabularx}{\linewidth}{X}
  \includegraphics[width=6cm]{TU_Logo_SW} \\\hline\hline
  \vspace{4.5em}
  \begin{singlespace}\begin{center}\bfseries\Huge  
  Squark Production in the $R$-Symmetric Supersymmetric Standardmodel  
  \end{center}\end{singlespace}
  \vspace{5.5em}
  \begin{singlespace}\begin{center}\large
   Masterarbeit \\ zur Erlangung des Hochschulgrades \\ 
   Master of Science \\ 
   im Master-Studiengang Physik
  \end{center}\end{singlespace}\medskip
  \begin{center}vorgelegt von\end{center}
  \begin{center}
   {\large Sebastian Liebschner} \\ geboren am 08.05.1990 in Meerane
  \end{center}\medskip
  \begin{singlespace}\begin{center}\large
   Institut für Kern- und Teilchenphysik \\
   Fachrichtung Physik \\
   Fakultät Mathematik und Naturwissenschaften \\
   Technische Universität Dresden \\ 2016
  \end{center}\end{singlespace}
 \end{tabularx}
\end{titlepage}

@@

% Gutachterseite
\thispagestyle{empty}\vspace*{48em}
Eingereicht am 15.~Juli~2016\\
Abgeänderte Fassung vom 18.~November~2016\vspace{1.5em}
\par{\large\begin{tabular}{ll}
 1. Gutachter: & Prof.~Dr.~Dominik Stöckinger \\
 2. Gutachter: & Prof.~Dr.~Arno Straessner \\
\end{tabular}}
\newpage
